IARC Technical Paper

### 2017-05-31 IARC_Paper/Paper.tex
Add risk reduction section

An added difficulty to the mission is that the setting is a Global Positioning System (GPS) denied environment. Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid. Thus, we determined that we needed to design other methods to determine our positioning. By using a camera to observe the gridlines and an Inertial Measurement Unit (IMU), we are working our way to determining where the vehicle is on the grid.

@@

>>>>

An added difficulty to the mission is that the setting is a Global Positioning System (GPS) denied environment. Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid. Thus, we determined that we needed to design other methods to determine our positioning. Our conceptional solution is to use a camera to observe the gridlines and an Inertial Measurement Unit (IMU) to determine where the vehicle is on the grid. Once we know that, we can have a computer vision program identify ground robots at risk of leaving the field.

@@

\subsection{Risk Reduction}
We took significant steps to ensure safe operation of the quadcopter. In order to keep the quadcopter from flying where we do not want, we have a Spektrum receiver module onboard so our designated pilot can manually control the vehicle. Additionally, we are able to check the status of the quadcopter through our telemetry to our ground station. The PX4 flight stack helps keep interference risk down through the EMI calibration on the Pixhawk. Additionally, logs from the Pixhawk showed us that vibration on the built quadcopter was well within recommended amounts.
